\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\setlength{\footskip}{4.35004pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{#1}\vspace{-2pt}
}

% \newcommand{\resumeMainHeading}[2]{
%   \vspace{-2pt}\item
%     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
%       \textbf{#1} & \small{#2} \\
%     \end{tabular*}\vspace{-5pt}
% }

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small{#2} \\
      \textit{\small{#3}} & \textit{\small{#4}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItemHeader}[1]{
    \item{\small{#1}}\vspace{-5pt}
}

\newcommand{\resumeItemFooter}[1]{
    \\ \vspace{7pt}\hspace{-0.35in}\footnotesize\emph{#1}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

%---------- CONSTANTS ----------

\def\myName{Ajaz Ur Rehman}
\def\myTitle{Software Engineer}
\def\myHometown{Bhopal, India}
\def\myEmail{ajazurrehman4@gmail.com}

%---------- LINKS ----------

\def\myPortfolio{https://ajaz-ur-rehman.github.io}
% \def\imgAllyLink{https://app.imgally.com}

%---------- DOCUMENT ----------

\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape \myName} \\ \vspace{3pt}
    \small
    \href{mailto:\myEmail}{ajazurrehman4@gmail.com}
    $|$
    \href{\myPortfolio}{ajaz-ur-rehman.github.io}
    $|$
    \href{tel:+917470611970}{+917470611970}
    $|$
    \myHometown\
\end{center}

%----------- Professional Summary -----------

\section{Professional Summary}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeItem{Full Stack Developer with 5 years of experience specializing in startups, greenfield projects, and SaaS products. Successfully launched two SaaS services, developed complex front-end applications for London-based startups, and contributed to a widely used SaaS platform adopted by thousands of users.}

\resumeSubHeadingListEnd

%----------- WORK EXPERIENCE -----------

\section{Work Experience}
\vspace{3pt}
\resumeSubHeadingListStart
\resumeSubheading
{Adsum-Works}{London, UK}
{Front-End Developer}{Jul 2022 - Sep 2023}
\resumeItemListStart
\resumeItem{Transitioned from backend to frontend development, taking over as the sole frontend developer, and reported directly to a backend-focused manager.}
\resumeItem{Rebuilt the entire frontend architecture from scratch, transitioning from legacy HTML and JavaScript code to a modern stack using React and Next.js, resulting in a more maintainable codebase.}
\resumeItem{Developed a custom KYC flow using React, integrating Veriff's API to handle media permissions and uploads, ensuring a seamless verification process without using traditional iframes.}
\resumeItem{Delivered the frontend application a month before schedule, including KYC, tax return calculations, and user dashboards with login, signup, and onboarding features.}
\resumeItem{Built a Chat-GPT-like interface for TaxAI, enabling users to interact with a chatbot for tax-related queries, and completed the project within one week.}
\resumeItem{Developed a UI component library with over 100 components based on Atomic Design Principles, collaborating with the UI/UX designer to translate Figma designs into code.}
\resumeItem{Collaborated with cross-functional teams, including designers, product managers, and the CTO, ensuring alignment with company goals and product vision.}
\resumeItem{Received personal recognition from the CEO for exceptional work ethic and consistently delivering projects ahead of deadlines.}
\resumeItemFooter{Skills: TypeScript, React.js, Next.js, Python, Flask, REST, Storybook, Material UI}
\resumeItemListEnd

\resumeSubheading
{SkootEco}{London, UK}
{Front-End Developer}{Dec 2021 - May 2022}
\resumeItemListStart
\resumeItem{Joined the company as a front-end developer, working alongside a senior developer under the guidance of a design-focused lead front-end developer and the CTO.}
\resumeItem{Created a central UI component library using Vue and Nuxt, developing around 50 reusable components to be used across all company projects.}
\resumeItem{Set up Storybook for the UI component library, facilitating collaboration with the product designer, product manager, and lead front-end developer.}
\resumeItem{Developed several micro-frontend pages, including login, signup, dashboard, and onboarding, within a micro-frontend architecture.}
\resumeItem{Wrote modular, maintainable code while ensuring responsiveness and accessibility across all devices, adhering to best practices for front-end development.}
\resumeItem{Utilized Formik for form validation and integrated checkout.com to enable secure payment processing.}
\resumeItem{Collaborated closely with the designer, translating designs into functional and accessible components.}
\resumeItemFooter{Skills: TypeScript, Vue.js, Nuxt.js, GraphQL, Storybook, TailwindCSS, CircleCI}
\resumeItemListEnd

\resumeSubheading
{AutomateMyApp}{\myHometown}
{Founder, and Full-Stack Developer}{Jan 2021 - Sep 2021}
\resumeItemListStart
\resumeItem{Designed and developed a workflow automation SaaS platform, similar to Zapier, enabling users to connect apps like Google Sheets, Calendly, and Discord.}
\resumeItem{Built the front end using Vue and Vite, and the back end with Node.js and Nest.js, deploying the service on AWS with PostgreSQL as the database.}
\resumeItem{Developed a custom no-code workflow builder, allowing users to create and manage automated workflows without needing to code.}
\resumeItem{Implemented OAuth-based authentication to securely access user accounts across various apps, enabling automated actions on their behalf.}
\resumeItem{Utilized JWT for user authentication and integrated social login options like Google and Facebook for simplified access.}
\resumeItem{Integrated PayPal for a subscription-based payment model, allowing users to easily subscribe to different service plans.}
\resumeItem{Successfully launched the service after 8 months of development, attracting users immediately after release.}
\resumeItemFooter{Skills: TypeScript, Vue.js, Vite, Node.js, Nest.js, PostgreSQL, AWS, Bootstrap}
\resumeItemListEnd

\resumeSubheading
{Clearalist}{\myHometown}
{Founder, and Full-Stack Developer}{Jan 2020 - Dec 2020}
\resumeItemListStart
\resumeItem{Designed and developed an email list cleaning and verification service, enabling users to upload and verify email lists in CSV format.}
\resumeItem{Built the front end using Vue and Vite, and the back end with Node.js and Express.js, utilizing MongoDB for database management and AWS for cloud services and deployment.}
\resumeItem{Implemented a custom authentication system with JWT tokens and cookies, ensuring secure login/signup and authorization processes.}
\resumeItem{Implemented automated end-to-end (E2E) testing for all API routes, ensuring the application functions correctly and enabling faster development without fear of introducing new bugs.}
\resumeItem{Successfully launched the SaaS application, which has verified over 5 million emails for thousands of users, including hundreds of paid users who frequently use the service.}
\resumeItem{Integrated PayPal for one-time payments, allowing users to purchase credits as needed for email verification.}
\resumeItemFooter{Skills: JavaScript, Express.js, Vue.js, Node.js, MongoDB, AWS, Bootstrap}
\resumeItemListEnd

\resumeSubheading
{Pabbly}{\myHometown}
{Web Developer}{Jan 2019 - Dec 2019}
\resumeItemListStart
\resumeItem{Joined as the only selected intern out of 30, quickly learning PHP and CodeIgniter on the job to contribute to the Email Marketing Service as part of a 4-developer team.}
\resumeItem{Fixed hundreds of bugs and issues by directly communicating with users, understanding their problems, and delivering effective solutions.}
\resumeItem{Chosen to develop a new and advanced Email Automation system, similar to MailerLite, enhancing the platform's capabilities and user experience.}
\resumeItem{Successfully migrated all users from the old automation system to the new one, ensuring zero downtime during the data transformation process in MySQL.}
\resumeItem{Authored comprehensive documentation for the Email Automation project, ensuring clarity and ease of maintenance for future developers.}
\resumeItem{Introduced Composer for PHP dependency management, replacing outdated manual installations, leading to a consistent and up-to-date codebase.}
\resumeItem{Optimized API calls and MySQL queries, resulting in a tenfold improvement in application performance and reducing the load on the server by 50\%.}
\resumeItemFooter{Skills: PHP, CodeIgniter, JavaScript, MySQL, HTML, CSS, Bootstrap}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------- PROJECTS -----------

% \section{Projects}
% \vspace{3pt}
% \resumeSubHeadingListStart

% \resumeMainHeading
% {ImgAlly -- \href{\imgAllyLink}{\imgAllyLink}}{Mar 2024 - May 2024}
% \resumeItemHeader{An AI-based image generation and editing tool utilizing an AI model API from HuggingFace.}
% \resumeItemListStart
% \resumeItem{Developed the backend with the Serverless framework and AWS Lambda, enabling cost-effective scaling.}
% \resumeItem{Implemented authentication with AWS Cognito, ensuring secure access to the application.}
% \resumeItem{Used AWS DynamoDB for user data storage and deployed the frontend with AWS S3 and CloudFront.}
% \resumeItemFooter{Skills: TypeScript, React.js, Next.js, TailwindCSS, Node.js, Serverless, AWS}
% \resumeItemListEnd

% \resumeSubHeadingListEnd

%----------- EDUCATION -----------

\section{Education}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
{Rajiv Gandhi Proudyogiki Vishwavidyalaya}{\myHometown}
{B.E. - Computer Science}{Jul 2013 - Jun 2017}

\resumeSubHeadingListEnd

%----------- CERTIFICATES -----------

% \section{Certificates}
% \resumeSubHeadingListStart

% \resumeSubheading
% {Enterprise Application Development for Cloud Deployment}{Oct 2016}
% {IBM}{\myHometown}
% \resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
\vspace{2pt}
\resumeSubHeadingListStart
\small{\item{

                \textbf{Languages:}{ JavaScript, TypeScript, PHP, Python} \\ \vspace{3pt}

                \textbf{Front-End:}{ React.js, Vue.js, Next.js, Nuxt.js, Vite} \\ \vspace{3pt}

                \textbf{Design Systems:}{ Material UI, TailwindCSS, Bootstrap} \\ \vspace{3pt}

                \textbf{Back-End:}{ Node.js, Express.js, Nest.js, Serverless} \\ \vspace{3pt}

                \textbf{Databases:}{ MySQL, PostgreSQL, MongoDB} \\ \vspace{3pt}

                \textbf{Testing:}{ Jest, Mocha, Chai, Supertest} \\ \vspace{3pt}

                \textbf{Cloud:}{ AWS, GCP, Azure, Digital Ocean} \\ \vspace{3pt}

                \textbf{Tools:}{ NPM, Storybook, Linux, Nginx, Git, Docker, Webpack, Babel, ESLint} \\ \vspace{3pt}

                \textbf{Others:}{ REST, GraphQL, OAuth, JWT, E2E Testing, CI/CD, Agile, Scrum} \\ \vspace{3pt}
          }}
\resumeSubHeadingListEnd

%----------- HOBBIES -----------

% \section{Hobbies}
% \resumeSubHeadingListStart
% \small{\item{Video Games, 3D Modeling, Hiking, Competitive Programming }}
% \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}