\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

%---------- CONSTANTS ----------

\def\myName{Ajaz Ur Rehman}
\def\myTitle{Software Engineer}
\def\myEmail{ajazurrehman4@gmail.com}
\def\myLinkedIn{https://linkedin.com/in/ajaz-ur-rehman}
\def\myGitHub{https://github.com/ajaz-ur-rehman}
\def\myPortfolio{https://ajaz-ur-rehman.github.io}
\def\myHometown{Bhopal, India}
\def\myHometownLocation{https://www.google.com/maps/place/Bhopal,+Madhya+Pradesh/@23.1996395,77.2410777,11z/data=!3m1!4b1!4m6!3m5!1s0x397c428f8fd68fbd:0x2155716d572d4f8!8m2!3d23.2599333!4d77.412615!16zL20vMGN3NTE?entry=ttu}

\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape \myName} \\ \vspace{3pt}
    \small
    \faAt \hspace{.5pt} \href{mailto:\myEmail}{Email}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{\myLinkedIn}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{\myGitHub}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} \href{\myPortfolio}{Portfolio}
    $|$
    \faMapMarker \hspace{.5pt} \href{\myHometownLocation}{\myHometown}
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {IES College of Technology
      }{\myHometown}
      {B.E. in Computer Science and Engineering;   \textbf{CGPA: 6.39/10}}{Aug 2013 \textbf{--} May 2017}
    
  \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{Languages:}{ JavaScript, TypeScript, Python, PHP, SQL, HTML, CSS} \\ \vspace{3pt}
        
        \textbf{Technologies:}{ Node.js, Express.js, Nest.js, Flask, React.js, Vue.js, Next.js, MySQL, MongoDB, Git, Docker, AWS} \\ \vspace{3pt}
        
        \textbf{Methodologies:}{ Agile, OOP, Functional Programming, DevOps, TDD} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd



%----------- EXPERIENCE -----------

\section{Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Adsum Works}{London, UK (Remote)}
      {Software Engineer}{Jul 2022 \textbf{--} Sep 2023, Full-time}
        \resumeItemListStart
            \resumeItem{Worked on the “Arçelik Digital Home Energy” project in a collaborative effort with DAI-Labor at the Technical University of Berlin under the supervision of \href{https://www.linkedin.com/in/prof-dr-dr-h-c-sahin-albayrak-65452a1/}{\color{blue}Prof. Dr. Şahin Albayrak}.}
            \resumeItem{Simulated discovery, pairing, and data exchange processes using the EEBUS protocol suite with C\# and Go. Migrated the framework from Go to C++ in order to ensure future adaptability for smart home IoT devices.}
            \resumeItem{Implemented the TLS protocol for secure data exchange using the X.509 standard and integrated multicast DNS for seamless communication to complement the development of SHIP and SPINE protocols.}
        \resumeItemListEnd

    \resumeSubheading
      {SKOOT}{London, UK (Remote)}
      {Front-End Engineer}{Dec 2021 \textbf{--} Jun 2022, Full-time}
        \resumeItemListStart
            \resumeItem{Engaged in collaborative research within the Robotics, Collectives and Learning subgroup at the Physical Intelligence Department with Ph.D. students \href{https://www.linkedin.com/in/sinan-ozgun-demir-981311129/}{\color{blue}Sinan Özgün Demir} and \href{https://www.linkedin.com/in/alpkaracakol/}{\color{blue}Alp Can Karacakol} on a project.}
            \resumeItem{Optimized a C++ ROS package for real-time conversion of 3D motion controller events to ROS messages, achieving high-frequency and buffer-free synchronization.}
            \resumeItem{Developed an Arduino Mega driver to activate a laser and pressure regulator, for monitoring coil temperatures and PID tuning to control the coil currents. Established a robust ROS-Arduino communication network.}
        \resumeItemListEnd
    
    \resumeSubheading
      {Magnet Brains}{\myHometown}
      {Web Developer}{Jan 2019 \textbf{--} Jan 2020, Full-time}
        \resumeItemListStart
            \resumeItem{Worked on the “Design and Implementation of Molecular Communication Systems Using Index Modulation” project under the supervision of \href{https://www.linkedin.com/in/alipusane/}{\color{blue}Prof. Dr. Ali Emre Pusane}.}
            \resumeItem{Simulated the Brownian motion of molecules in a SISO MCvD system and predicted simulation parameters such as receiver radius, diffusion coefficient, and transmitter-receiver distance using CNNs with Keras and TensorFlow.}
            \resumeItem{Plotted the arrival of molecules per symbol duration in a SISO MCvD system using Binomial, Poisson, and Gaussian model approximations with MATLAB.}
        \resumeItemListEnd

    \resumeSubheading
      {Magnet Brains}{\myHometown}
      {Web Developer Intern}{Nov 2018 \textbf{--} Jan 2019, Internship}
        \resumeItemListStart
            \resumeItem{Executed diverse NLP tasks, including NER, POS tagging, sentiment analysis, text classification, and extractive and generative QA using transformers and Hugging Face libraries.}
            \resumeItem{Developed a generative QA system with dense passage retrieval (DPR) and retrieval-augmented generation (RAG) techniques using the Haystack framework and PyTorch.}
            \resumeItem{Worked on a Turkish open-domain QA system made by fine-tuning BERTurk and XLM-Roberta models. Tabularized exact match and F1 scores derived from DeepMind's XQuAD and various Turkish data sets.}
        \resumeItemListEnd

    \resumeSubheading
      {Rainbow Western}{\myHometown}
      {Android Developer Intern}{Oct 2017 \textbf{--} Nov 2017, Internship}
        \resumeItemListStart
            \resumeItem{Designed and simulated numerous analog circuits such as voltage-mode controlled buck converter, phase-shifted full-bridge isolated DC-DC converter, and EMI filters with LTspice.}
            \resumeItem{Researched real-world compatible electronic components to be used in such circuits including GaNFETs, high-side gate drivers, and Schottky diodes.}
            \resumeItem{Assembled PCBs of both common and differential mode filters and used VNA Bode 100 to measure the cut-off frequencies.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%----------- PROJECTS -----------

\section{SaaS Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{ImgAlly} $|$ \emph{\href{https://github.com/arasgungore/filters-and-fractals}{\color{blue}Live}}}{}
          \resumeItemListStart
            \resumeItem{A C project which implements a variety of image processing operations that manipulate the size, filter, brightness, contrast, saturation, and other properties of PPM images from scratch and recursive fractal generation functions to model popular fractals including Mandelbrot set, Julia set, Koch curve, Barnsley fern, and Sierpinski triangle.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{AutomateMyApp} $|$ \emph{\href{https://github.com/arasgungore/chess-bot}{\color{blue}Live}}}{}
          \resumeItemListStart
            \resumeItem{A C++ project in which you can play chess against an AI with a specified decision tree depth that uses alpha-beta pruning algorithm to predict the optimal move. Aside from basic moves, this mini chess engine also implements chess rules such as castling, en passant, fifty-move rule, threefold repetition, and pawn promotion.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Clearalist} $|$ \emph{\href{https://github.com/arasgungore/CMPE250-projects}{\color{blue}Live}}}{}
          \resumeItemListStart
            \resumeItem{Five Java projects that apply DS\&A concepts such as discrete-event simulation using priority queues, Dijkstra's shortest path algorithm, Prim's algorithm to find the minimum spanning tree, Dinic's algorithm for maximum flow problems, and weighted job scheduling with dynamic programming to real-world problems.}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd

%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{High Honors Degree:}{ Awarded to Bachelor alumni who have graduated with a GPA greater than or equal to 3.50 by Boğaziçi University. (Jul 2023)} \\ \vspace{3pt}

        \textbf{TÜBİTAK 2247-C Intern Researcher Scholarship:}{ Awarded to students who take part in research projects carried out by the Scientific and Technological Research Council of Turkey (TÜBİTAK). (Dec 2021 \textbf{--} Jun 2022)} \\ \vspace{3pt}
    
        % \textbf{National University Admission Exam (YKS):}{ Ranked $75^{th}$ in Mathematics and Science among ca. 2.3 million candidates with a test score of 489.92/500. (Jul 2018)} \\ \vspace{3pt}
        
        \textbf{KYK Outstanding Success Scholarship:}{ Awarded to students who have been ranked in the top 100 on National University Admission Exam by Higher Education Credit and Hostels Institution (KYK). (Sep 2018 \textbf{--} Jun 2023)} \\ \vspace{3pt}
        
        % \textbf{Boğaziçi University Success Scholarship:}{ Awarded to students who have been ranked in the top 100 on National University Admission Exam by Boğaziçi University. (Sep 2018 \textbf{--} Jun 2023)} \\ \vspace{3pt}
        
        \textbf{Kocaeli Science High School Valedictorian Award:}{ Graduated as the highest ranked student. (Jun 2018)}
    }}
  \resumeSubHeadingListEnd



%----------- RELEVANT COURSEWORK -----------

% \section{Relevant Coursework}
  % \vspace{2pt}
  % \resumeSubHeadingListStart
    % \small{\item{
        % \textbf{Major coursework:}{ Materials Science, Electrical Circuits I-II, Digital System Design, Numerical Methods, Probability Theory, Electronics I-II, Signals and Systems, Electromagnetic Field Theory, Energy Conversion, System Dynamics and Control, Communication Engineering, Pattern Recognition, Introduction to Digital Signal Processing, Introduction to Digital Communications, Introduction to Database Systems, Introduction to Image Processing, Machine Vision} \\ \vspace{3pt}
        
        % \textbf{Minor coursework:}{ Discrete Computational Structures, Introduction to Object-Oriented Programming, Data Structures and Algorithms, Computer Organization, Fundamentals of Software Engineering}
    % }}
  % \resumeSubHeadingListEnd



%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Project Management and Personal Productivity}
    
  % \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

% \section{Organizations}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}
    
  % \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Basketball, Swimming, Fitness, Eight-ball, Horology}}
  % \resumeSubHeadingListEnd



%----------- REFERENCES -----------

% \section{References}
  % \vspace{2pt}
  % \resumeSubHeadingListStart
    % \item{References available upon request.}
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}