\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

% -------------------- FONT OPTIONS --------------------
% sans-serif
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% serif
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.35004pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

\begin{center}
    \textbf{\Huge \scshape Ajaz Ur Rehman} \\ \vspace{8pt}
    \small 
    \faIcon{code}
    \href{https://ajaz-ur-rehman.github.io}
    {ajaz-ur-rehman.github.io} $  $
    \faIcon{github}
    \href{https://github.com/ajaz-ur-rehman}{github.com/ajaz-ur-rehman} $  $
    \faIcon{envelope}
    \href{mailto:ajazurrehman4@gmail.com}
    {ajazurrehman4@gmail.com}
    \faIcon{phone}
    \href{tel:+917470611970}{+91 7470611970} $  $
\end{center}

% -------------------- Experience --------------------
\section{Work Experience}
    \resumeSubHeadingListStart

        \resumeSubheading
          {Adsum Works}{London, UK}
          {Front End Developer (Remote) $|$ \footnotesize\emph{React, Next, TypeScript, Python, Flask, Material UI}}{Jul 2022 - Sep 2023}
        \resumeItemListStart
            \resumeItem{Implemented a user identity verification flow using the camera on Android, iPhone, Mac, and PC.}
            \resumeItem{Developed the entire front-end using Next, while migrating old live pages incrementally.}
            \resumeItem{Created the UI library using Next and Storybook, by collaborating with the UI/UX designer.}
          \resumeItemListEnd

        \resumeSubheading
          {SKOOT}{London, UK}
          {Front End Developer (Remote) $|$ \footnotesize\emph{Vue, Nuxt, TypeScript, Tailwind, GraphQL, Hugo}}{Dec 2021 - May 2022}
        \resumeItemListStart
            \resumeItem{Built 50+ UI library components based on designs, and published them on Storybook.}
            \resumeItem{Developed the dashboard, user profile, and payment pages of the application using Nuxt.}
            \resumeItem{Integrated checkout.com payment gateway, Formik form validations, and TailwindCSS.}
          \resumeItemListEnd

        \resumeSubheading
          {Pabbly}{Bhopal, India}
          {Web Developer $|$ \footnotesize\emph{HTML/CSS, JavaScript, PHP, CodeIgniter, jQuery, MySQL}}{Jan 2019 - Dec 2019}
        \resumeItemListStart
            \resumeItem{Developed the Email Automation project and integrated it into the Email Marketing application.}
            \resumeItem{Migrated users of the old automation system on the live server with zero downtime.}
            \resumeItem{Optimized MySQL queries, and introduced Composer for dependency management.}
        \resumeItemListEnd
          
    \resumeSubHeadingListEnd
    
% -------------------- PROJECTS --------------------
\section{Projects}
    \resumeSubHeadingListStart

        \resumeSubheading
          {Clearalist}{\href{https://clearalist.com}{clearalist.com} $  $}
          {Full Stack Developer $|$ \footnotesize\emph{Vue, Node, JavaScript, Express, MongoDB, AWS, Nginx, Figma}}{Jan 2020 - Dec 2020}
        \resumeItemListStart
            \resumeItem{Designed, developed, and deployed a SaaS application for bulk email verification.}
            \resumeItem{Integrated PayPal, added affiliate system, and user emails using SES, and implemented E2E testing.}
            \resumeItem{Implemented job processing using SQS queues to handle multiple file uploads reliably.}
          \resumeItemListEnd

        \resumeSubheading
          {AutomateMyApp}{\href{https://automatemyapp.com}{automatemyapp.com} $  $}
          {Full Stack Developer $|$ \footnotesize\emph{Vue, Node, TypeScript, Nest, PostgreSQL, AWS, Nginx, Figma}}{Jan 2021 - Sep 2021}
        \resumeItemListStart
            \resumeItem{Designed, developed, and deployed a SaaS application for workflow automation.}
            \resumeItem{Integrated PayPal and added OAuth 2.0-based social login, webhooks, and UI-based workflow editor.}
            \resumeItem{Added 10+ popular services as integrations for users and deployed the application using AWS.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd

% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {IES College of Technology}{Bhopal, India}
      {B.E (Computer Science)}{Jun 2013 - Jun 2017}

  \resumeSubHeadingListEnd

% -------------------- SKILLS --------------------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    
     \textbf{Languages}{: JavaScript, TypeScript, PHP, Python, Java, and HTML/CSS.}
     
     \textbf{Front-End}{: React, Vue, Vite, Next, Nuxt, Material UI, Tailwind, Bootstrap, and jQuery.}

     \textbf{Back-End}{: Node, Express, Nest, Serverless, Flask, CodeIgniter, and GraphQL.}

     \textbf{Database}{: MySQL, PostgreSQL, MongoDB, DynamoDB, SQLite, and Redis.}

     \textbf{Cloud}{: AWS, Azure, GCP, Heroku, Digital Ocean, and CloudFlare.}
     
     \textbf{Tools}{: Git/GitHub, Docker, Linux, Babel, Storybook, Webpack, VS Code, Nginx, PM2, and Figma.}
     
    }}
 \end{itemize}

\end{document}
