\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\setlength{\footskip}{4.35004pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

%---------- CONSTANTS ----------

\def\myName{Ajaz Ur Rehman}
\def\myTitle{Software Engineer}
\def\myEmail{ajazurrehman4@gmail.com}
\def\myLinkedIn{https://linkedin.com/in/ajaz-ur-rehman}
\def\myGitHub{https://github.com/ajaz-ur-rehman}
\def\myPortfolio{https://ajaz-ur-rehman.github.io}
\def\myHometown{Bhopal, India}
\def\myHometownLocation{https://google.com/maps/place/Bhopal,+Madhya+Pradesh/@23.1996395,77.2410777,11z/data=!3m1!4b1!4m6!3m5!1s0x397c428f8fd68fbd:0x2155716d572d4f8!8m2!3d23.2599333!4d77.412615!16zL20vMGN3NTE?entry=ttu}

\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape \myName} \\ \vspace{3pt}
    \small
    \faAt \hspace{.5pt} \href{mailto:\myEmail}{Email}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{\myLinkedIn}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{\myGitHub}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} \href{\myPortfolio}{Portfolio}
    $|$
    \faMapMarker \hspace{.5pt} \href{\myHometownLocation}{\myHometown}
\end{center}

%----------- SKILLS -----------

\section{Skills}
\vspace{2pt}
\resumeSubHeadingListStart
\small{\item{

                \textbf{Languages:}{ JavaScript, TypeScript, Python, PHP, SQL, HTML, CSS} \\ \vspace{3pt}

                \textbf{Technologies:}{ Node.js, Express.js, Nest.js, Flask, React.js, Vue.js, Next.js, MySQL, MongoDB} \\ \vspace{3pt}

                \textbf{Methodologies:}{ Agile, OOP, Functional Programming, DevOps, TDD} \\ \vspace{3pt}

                \textbf{Others:}{ Docker, Linux, Nginx, PM2, Git, AWS, GCP} \\ \vspace{3pt}

          }}
\resumeSubHeadingListEnd

%----------- EXPERIENCE -----------

\section{Experience}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
{Adsum}{London, UK (Remote)}
{Software Engineer}{Jul 2022 \textbf{--} Sep 2023, Full-time}
\resumeItemListStart
\resumeItem{Developed an automated custom KYC flow using \href{https://veriff.com}{\color{blue}Veriff}, enabling user identity and document verification without human intervention, applicable on both web and mobile platforms.}
\resumeItem{Implemented the entire front end from scratch, including multiple onboarding flows for different use cases, user dashboards, tax reclaim, status pages, and a chat interface for our \href{https://chat.taxai.uk}{\color{blue}Tax AI} bot.}
\resumeItem{Deployed the front end using a custom build pipeline through Flask API, facilitating the migration of old HTML pages to the new front end without disrupting the user experience.}
\resumeItemListEnd

\resumeSubheading
{SKOOT}{London, UK (Remote)}
{Front-end Developer}{Dec 2021 \textbf{--} May 2022, Full-time}
\resumeItemListStart
\resumeItem{Developed a UI component library based on Figma designs with over 50 reusable components using Vue.js, enhancing development efficiency and design consistency across the platform.}
\resumeItem{Created responsive and accessible web pages, including login, onboarding, dashboard, user profile, and payment, based on a \href{https://chat.taxai.uk}{\color{blue}Micro Frontend} architecture. Used GraphQL API to fetch and mutate user data.}
\resumeItem{Integrated checkout.com for payments, Formik for form validations, and Hugo to generate a static site - improving the marketing website's performance and SEO.}
\resumeItemListEnd

\resumeSubheading
{Magnet Brains}{\myHometown}
{Web Developer}{Jan 2019 \textbf{--} Dec 2019, Full-time}
\resumeItemListStart
\resumeItem{Worked on \href{https://www.pabbly.com/email-marketing}{\color{blue}Pabbly Email Marketing} platform and led the development of \href{https://youtube.com/watch?v=kkopsVYOO7Y}{\color{blue}Email Automation} project, enabling users to automate their email campaigns based on custom triggers and actions.}
\resumeItem{Migrated data of over 1,000 users from the old automation system to the new one with zero downtime, ensuring a smooth transition and improved user workflows.}
\resumeItem{Optimized MySQL queries and introduced Composer for dependency management, reducing API data fetching speed by up to 10 times and decreasing server load by 50\%.}
\resumeItemListEnd

\resumeSubheading
{Magnet Brains}{\myHometown}
{Web Developer Intern}{Nov 2018 \textbf{--} Dec 2018, Internship}
\resumeItemListStart
\resumeItem{Competed with 500 applicants in a 3-month internship program and secured a full-time position by completing all challenges on time and with high quality.}
\resumeItem{Wrote a PHP script to check email reputation that can call over 100 APIs in parallel and fetch data in just a few seconds, compared to an old script that took over 3 minutes.}
\resumeItemListEnd

\resumeSubheading
{Rainbow Western}{\myHometown}
{Android Developer Intern}{Oct 2017 \textbf{--} Nov 2017, Internship}
\resumeItemListStart
\resumeItem{Developed and published an Android app for buying hotel membership plans to access exclusive features, increasing revenue by 200\%.}
\resumeItem{Developed and published an Android app for a local NGO to help orphaned children receive donations, increasing donations by 50\%.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------- PROJECTS -----------

\section{SaaS Projects}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Clearalist} $|$ \emph{\href{https://clearalist.com}{\color{blue}Website}}}{}
\resumeItemListStart
\resumeItem{Clearalist is an Email List cleaning service that allows users to upload their email lists and get them verified. This app has served over 1,000 customers and processed over 5 million emails. It uses Telnet and SMTP protocols to verify emails and has a 90\% accuracy rate.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{AutomateMyApp} $|$ \emph{\href{https://automatemyapp.com}{\color{blue}Website}}}{}
\resumeItemListStart
\resumeItem{AutomateMyApp is a workflow automation tool that allows users to create custom workflows using a drag-and-drop interface. It supports many popular services like Gmail, Google Sheets, Calendly, and Discord. The tool uses OAuth 2.0 for app authorization and webhooks for efficient trigger handling.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{ImgAlly} $|$ \emph{\href{https://imgally.com}{\color{blue}Website}}}{}
\resumeItemListStart
\resumeItem{ImgAlly is an AI-based image editing tool that allows users to upload and edit images. It uses an AI model API by HuggingFace and features a user-friendly interface. The tool is deployed on AWS and utilizes a serverless architecture.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------- EDUCATION -----------

\section{Education}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
{IES College of Technology}{\myHometown}
% {B.E. in Computer Science and Engineering;   \textbf{CGPA: 6.39/10}}{Aug 2013 \textbf{--} May 2017}
{B.E. in Computer Science and Engineering}{Aug 2013 \textbf{--} May 2017}

\resumeSubHeadingListEnd

%----------- CERTIFICATES -----------

\section{Certificates}
\resumeSubHeadingListStart

\resumeOrganizationHeading
{IBM Training}{Oct 2016}{Enterprise Application Development for Cloud Deployment}

\resumeSubHeadingListEnd

%----------- AWARDS & ACHIEVEMENTS -----------

% \section{Achievements}
% \vspace{2pt}
% \resumeSubHeadingListStart

% \resumeOrganizationHeading
% {High School Chess Winner}{Oct 2010}{Hind Convent H.S. School.}

% \resumeSubHeadingListEnd



%----------- RELEVANT COURSEWORK -----------

% \section{Relevant Coursework}
% \vspace{2pt}
% \resumeSubHeadingListStart
% \small{\item{
% \textbf{Major coursework:}{ Materials Science, Electrical Circuits I-II, Digital System Design, Numerical Methods, Probability Theory, Electronics I-II, Signals and Systems, Electromagnetic Field Theory, Energy Conversion, System Dynamics and Control, Communication Engineering, Pattern Recognition, Introduction to Digital Signal Processing, Introduction to Digital Communications, Introduction to Database Systems, Introduction to Image Processing, Machine Vision} \\ \vspace{3pt}

% \textbf{Minor coursework:}{ Discrete Computational Structures, Introduction to Object-Oriented Programming, Data Structures and Algorithms, Computer Organization, Fundamentals of Software Engineering}
% }}
% \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

% \section{Organizations}
% \resumeSubHeadingListStart

% \resumeOrganizationHeading
% {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}

% \resumeSubHeadingListEnd



%----------- HOBBIES -----------

\section{Hobbies}
\resumeSubHeadingListStart
\small{\item{Video Games, 3D Modelling, Movies, TV Shows, Anime, Hiking, Competitive Programming }}
\resumeSubHeadingListEnd



%----------- REFERENCES -----------

% \section{References}
% \vspace{2pt}
% \resumeSubHeadingListStart
% \item{References available upon request.}
% \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}